\section{IndexCard RPG}\label{indexcard-rpg}

Tabletop RPG rules that fit on a single 5x3 inch index card.

Materials required:

\begin{itemize}
\tightlist
\item
  paper
\item
  writing utensil
\item
  six-sided die.
\end{itemize}

Please offer elegant summaries of these rules!

Lillian Lemmer, Catlin T

\section{Core Ruleset}\label{core-ruleset}

Start with: 10 HEARTS, 1 BAM, 1 EVADE, 3 CRIT, and 6 points to
distribute; point adds 3 to CRIT and 5 to HEARTS.

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Player with highest EVADE rolls first

  \begin{itemize}
  \tightlist
  \item
    Roll 6 or 5: +CRIT BAM bonus, skip step 2
  \item
    Roll 1: miss, skip to step 4
  \end{itemize}
\item
  Defender rolls up to their EVADE times, if roll 6 skip step 3
\item
  Defender loses HEARTS equal to attacker's BAM plus possible bonuses
\item
  Start at step \#1, but rotate players in order of EVADE
\end{enumerate}

Rules for creating supplemental rulesets:

\begin{itemize}
\tightlist
\item
  Fits on index card (5x3 inches)
\item
  8 point Inconsolata Regular font
\item
  List required supplements on top, e.g.,
  \texttt{REQUIRED:\ Usable\ Items}
\end{itemize}

\section{Supplement Ruleset: Usable
Items}\label{supplement-ruleset-usable-items}

Must announce which item used before rolling.

Players can use an item before they attack.

Characters start with one item:

\begin{itemize}
\tightlist
\item
  CANDY: restore \texttt{ROLL} \texttt{HEARTS}, if roll 1 or 2 restore
  full health.
\item
  SODA: +ROLL BAM bonus, unevadeable
\end{itemize}

Items for co-op only:

\begin{itemize}
\tightlist
\item
  TOKEN: acts as a roll of 6; can attack
\item
  MOLOTOV: Damage is 2x roll; unevadable
\item
  THROWING STARS: Roll thrice, the total is unevadable damage.
\end{itemize}

\section{Supplement Ruleset: Path
Cards}\label{supplement-ruleset-path-cards}

\texttt{REQUIRES:\ Usable\ Items}

A novel is a series of cards which have a scenario and options. Write
the story, where each option may have \texttt{REQUIREMENTS} and
\texttt{EVENTS}.

Option \texttt{REQUIREMENTS}:

\begin{itemize}
\tightlist
\item
  \texttt{USE\ x}: Item \texttt{x} is required for this option.
\item
  \texttt{CHECK\ stat\ x\ FAIL\ y}: Option requires \texttt{stat} +
  \texttt{roll} to at least be \texttt{x}, else \texttt{FAIL} event
  \texttt{y}. Example: use for conversation,
  \texttt{"You\textquotesingle{}re\ looking\ pretty!"\ CHECK\ HEARTS\ 20\ FAIL\ BATTLE}
\end{itemize}

Option \texttt{EVENTS}:

\begin{itemize}
\tightlist
\item
  \texttt{OPEN}: Get item \#ROLL from the chest on the back of this path
  card
\item
  \texttt{BATTLE}: Battle monster on the back of this path card
\item
  \texttt{NEXTCARD}: select random path card from this novel
\end{itemize}

Preface non-required things which require a supplement with
\texttt{SUPPLEMENT\ supplement\ card\ name}.

Use die roll to determine who the monster attacks.

\section{Path Card: Sleeping Ugly
(Front)}\label{path-card-sleeping-ugly-front}

You are in a room with a slumbering troll, a locked door, and a treasure
chest.

To get to the chest, you must either tip-toe around the troll or fight
it.

\begin{itemize}
\tightlist
\item
  Sneak around Troll and \texttt{OPEN} the chest
  (\texttt{CHECK\ evade\ 14\ FAIL\ BATTLE})
\item
  \texttt{BATTLE} the Troll and \texttt{OPEN} the chest
\item
  Go to door and \texttt{USE\ key} (\texttt{NEXTCARD})
\end{itemize}

\section{Path Card: Sleeping Ugly
(Back)}\label{path-card-sleeping-ugly-back}

Troll - H: 16 (48) - B: 14 - E: 1 - C: 4 (8) Drops: Key

Treasure Chest 1. KEY 2. TOKEN 3. MOLOTOV 4. THROWING STARS 5. CANDY 6.
SODA

\section{Path Card: Monk Up Your Mind
(Front)}\label{path-card-monk-up-your-mind-front}

You come across a meditating monk sitting in front of two doors.

\begin{itemize}
\tightlist
\item
  ``Philosophical banter here'' CHECK STAT HEARTS 17 FAIL GAME OVER
\item
  BATTLE MONK
\item
  LEFT DOOR
\item
  RIGHT DOOR
\end{itemize}

\section{Path Card: Monk Up Your Mind
(Back)}\label{path-card-monk-up-your-mind-back}

MONK - H: 20 - B: 5 - E: 24 - C: 12
